Compare label transfer results between Azimuth and Azimuth-adapted strategy

### 2024-11-05 analyses/cell-type-wilms-tumor-06/supplemental-notebooks/compare-label-transfer-approaches.Rmd

  fetal_full <- srat_objects |>
    purrr::imap(
      \(srat, id) {
        # Perform label transfer with new code
        set.seed(params$seed)
        query <- prepare_query(srat, rownames(full_reference), file.path(module_base, "scratch", "homologs.rds"))
        query <- transfer_labels(
          query,
          full_reference,
          full_dims,
          full_refdata
        )

@@

  fetal_kidney <- srat_objects |>
    purrr::imap(
      \(srat, id) {
        # Perform label transfer with new code
        set.seed(params$seed)
        query <- prepare_query(srat, rownames(kidney_reference), file.path(module_base, "scratch", "homologs.rds"))
        query <- transfer_labels(
          query,
          kidney_reference,
          kidney_dims,
          kidney_refdata
        )

@@

| Sample | Reference | Count | Azimuth | Azimuth-adapted |
|--------|-----------|-------|---------|-----------------|
| SCPSC000179 | L1 | 70 | Metanephritic cells | Intestinal epithelial cells | 
| SCPSC000179 | Organ | 64 | Kidney | Intestine | 
| SCPSC000179 | Organ | 20 | Lung | Kidney | 
| SCPSC000194 | L1 | 60 | Stromal cells | Mesangial cells | 
| SCPSC000194 | Organ | 35 | Kidney | Intestine | 
| SCPSC000194 | Organ | 36 | Lung | Kidney | 
| SCPSC000205 | Organ | 56 | Kidney | Intestine |
| SCPSC000208 | L1 | 101 | Mesangial cells | Metanephritic cells |  
| SCPSC000208 | L1 | 101 | Intestinal epithelial cells | Metanephritic cells |  
| SCPSC000208 | Organ | 149 | Kidney | Intestine |

@@

- There are a small but notable number of cells flipped between mesenchyme and kidney cells, in particular for sample SCPSC000184.
This is the main discrepancy.
- Most of the cell type differences are not necessarily biologically meaningful for our purposes, as listed below. These are not noted in the table.
   - `kidney cell` vs `podocyte`
   - `kidney epithelial cell` vs `kidney cell` 
   - `mesenchymal cell` vs `mesenchymal stem cell` 
- There are a decent number of times when stroma and fetal nephron are flipped, but this makes sense given that we expect many of the stroma may be tumor.
- Disagreeing annotation scores when using the cell type reference were often higher, but many of the disagreements for this reference were not meaningful (e.g. `kidney epithelial cell` vs `kidney cell`).

| Sample | Reference | Count | Azimuth | Azimuth-adapted |
|--------|-----------|-------|---------|-----------------|
| SCPSC000179 | cell type | 202 | mesenchymal cell | kidney epithelial cell | 
| SCPSC000184 | compartment | 111 | fetal nephron |  stroma | 
| SCPSC000184 | cell type | 536 | kidney epithelial cell | mesenchymal cell | 
| SCPSC000194 | compartment | 565 | fetal nephron |  stroma | 
| SCPSC000194 | cell type  | 89 | kidney epithelial cell | mesenchymal cell | 
| SCPSC000205 | compartment  | 684 | fetal nephron |  stroma | 
| SCPSC000208 | compartment  | 2111 | fetal nephron |  stroma |

>>>>

  # Perform label transfer with new code
  assay <- "RNA"
  fetal_full <- srat_objects |>
    purrr::imap(
      \(srat, id) {
        set.seed(params$seed)

        query <- prepare_query(
          srat,
          rownames(full_reference),
          assay,
          file.path(module_base, "scratch", "homologs.rds")
        )
        query <- transfer_labels(
          query,
          full_reference,
          full_dims,
          full_refdata,
          query.assay = assay
        )

@@

  # Perform label transfer with new code
  assay <- "RNA"
  fetal_kidney <- srat_objects |>
    purrr::imap(
      \(srat, id) {
        set.seed(params$seed)

        query <- prepare_query(
          srat,
          rownames(kidney_reference),
          assay,
          file.path(module_base, "scratch", "homologs.rds")
        )
        query <- transfer_labels(
          query,
          kidney_reference,
          kidney_dims,
          kidney_refdata,
          query.assay = assay
        )

@@

| Sample | Reference | Count | Azimuth | Azimuth-adapted |
|--------|-----------|-------|---------|-----------------|
| SCPSC000179 | L1 | 70 | Metanephritic cells | Intestinal epithelial cells | 
| SCPSC000179 | Organ | 64 | Kidney | Intestine | 
| SCPSC000179 | Organ | 20 | Lung | Kidney | 
| SCPSC000194 | L1 | 60 | Stromal cells | Mesangial cells | 
| SCPSC000194 | Organ | 35 | Kidney | Intestine | 
| SCPSC000194 | Organ | 36 | Lung | Kidney | 
| SCPSC000205 | Organ | 56 | Kidney | Intestine |
| SCPSC000208 | L1 | 101 | Mesangial cells | Metanephritic cells |  
| SCPSC000208 | L1 | 75 | Intestinal epithelial cells | Metanephritic cells |  
| SCPSC000208 | Organ | 149 | Kidney | Intestine |

@@

- Most of the cell type differences are not in the table below because they are not necessarily biologically meaningful for our purposes:
   - `kidney cell` vs `podocyte`
   - `kidney epithelial cell` vs `kidney cell` 
   - `mesenchymal cell` vs `mesenchymal stem cell`

| Sample | Reference | Count | Azimuth | Azimuth-adapted |
|--------|-----------|-------|---------|-----------------|
| SCPSC000179 | cell type | 94 | mesenchymal cell | kidney epithelial cell | 
| SCPSC000205 | compartment  | 52 | fetal nephron |  stroma |
